Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-10-02 ms/ms.Rmd
ms: predictor classes + radiometric surveys

>>>>

We created the same suite of 25 quantitative peat depth predictors for both sites.
All predictors were derived either from an airborne radiometric survey or from a digital terrain model.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the digital terrain models we calculated several simple terrain variables and a series of more complex geomorphometric and hydrological variables.

The radiometric survey covering Skrimfjella was conducted in 2008--2011. 
The survey was flown at an average altitude of \unit{75\,m} and average speed of \unit{108\,km\,h^{-1}}, with flight lines spaced \unit{200\,m} apart.
Spectrometer count rates were calibrated annually to known concentrations of Potassium, Thorium, and Uranium in mobile pads.
The Geological Survey of Norway processed data from the spectrometer following standard procedures outlined by the International Atomic Energy Association, and the processing included: correction for aircraft and cosmic background radiation, correction for radon in the air, window stripping of the gamma ray spectrum, correction for flying height, conversion of count rates to ground concentrations, and finally gridding to \unit{50\,m} resolution with micro-leveling.
Further details about the survey and data processing are provided in Baranwal et al. [-@baranwalHelicopterborneMagneticElectromagnetic2013].

A very similar radiometric survey covering Ørskogfjellet was conducted in December 2014 and January 2015. 
This survey was flown at an average altitude of \unit{80\,m} and average speed of \unit{88\,km\,h^{-1}}, with flight lines also spaced \unit{200\,m} apart.
Spectrometer count rates were calibrated in 2013 to known concentrations of Potassium, Thorium, and Uranium in mobile pads.
The spectrometer data were processed following the same procedure as for the survey at Skrimfjella, except that a convolution filter was added to smoothen the gridded data.
Further details about the survey and data processing are provided in Ofstad [-@ofstadHelicopterborneMagneticRadiometric2015].

### 2024-10-02 ms/ms.tex
ms: predictor classes + radiometric surveys

>>>>

We created the same suite of 25 quantitative peat depth predictors for both sites.
All predictors were derived either from an airborne radiometric survey or from a digital terrain model.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the digital terrain models we calculated several simple terrain variables and a series of more complex geomorphometric and hydrological variables.

The radiometric survey covering Skrimfjella was conducted in 2008--2011.
The survey was flown at an average altitude of \unit{75\,m} and average speed of \unit{108\,km\,h^{-1}}, with flight lines spaced \unit{200\,m} apart.
Spectrometer count rates were calibrated annually to known concentrations of Potassium, Thorium, and Uranium in mobile pads.
The Geological Survey of Norway processed data from the spectrometer following standard procedures outlined by the International Atomic Energy Association, and the processing included: correction for aircraft and cosmic background radiation, correction for radon in the air, window stripping of the gamma ray spectrum, correction for flying height, conversion of count rates to ground concentrations, and finally gridding to \unit{50\,m} resolution with micro-leveling.
Further details about the survey and data processing are provided in Baranwal et al. \citeyearpar{baranwalHelicopterborneMagneticElectromagnetic2013}.

A very similar radiometric survey covering Ørskogfjellet was conducted in December 2014 and January 2015.
This survey was flown at an average altitude of \unit{80\,m} and average speed of \unit{88\,km\,h^{-1}}, with flight lines also spaced \unit{200\,m} apart.
Spectrometer count rates were calibrated in 2013 to known concentrations of Potassium, Thorium, and Uranium in mobile pads.
The spectrometer data were processed following the same procedure as for the survey at Skrimfjella, except that a convolution filter was added to smoothen the gridded data.
Further details about the survey and data processing are provided in Ofstad \citeyearpar{ofstadHelicopterborneMagneticRadiometric2015}.
